Replicator-mutator and noise-perturbed replicator dynamics

### 2014-11-05 snippets/Nosofsky_similarity.Rmd
paper shortened, and plots resized/rearranged

ggsave(p, file="paper/plots/NosofskySim.pdf", width=7, height=4)

>>>>

ggsave(p, file="paper/plots/NosofskySimConf.pdf", width=7, height=4)

simDF = subset(simDF, simDF$normalized == "Nosofsky similarity")

p = ggplot(simDF, aes(x = distance, y = similarity, shape = alpha_i))+
  geom_line(color='grey')  + geom_point()  + 
  ylab("") + 
  xlab("distance in physical space") +
  scale_shape_discrete(name="imprecision")

ggsave(p, file="paper/plots/NosofskySim.pdf", width=6, height=2.25)
